TacticToe: Learning the Game of Tactics

### 2018-02-19 tactictoe_jv.tex
minor

\begin{itemize}
\item Proof recording at the tactic level is made more precise. Pattern
matching constructions, opening of submodules are supported. The different
recording steps (parsing, unfolding and replaying) are regrouped into a single
\sml function.
\item Monte Carlo tree search~~\cite{montecarlo} (MCTS) replaces A* as our
search algorithm. The MCTS algorithm gives a more balanced feedback on
the success of
each proof step by
comparing subtrees of the search tree instead of leafs. The policy and
evaluation are learned
through supervised learning.
\item Proof guidance required by MCTS is given by predictors for
three kinds of objects: tactics, theorems and lists of goals.
\item The orthogonalization process that eliminates redundant tactics is 
described in a precise manner.
\item A tactic abstraction mechanism is introduced. It enables us to create
more general and flexible tactics where tactic arguments are dynamically
predicted.
\item The internal ATP \metis is complemented
by asynchronous calls to \eprover to help \tactictoe during proof search.
\item First evaluation of \tactictoe success rate relative to
the length of the original human proofs.
\item Minimization and prettification of the generated proof improves user 
interaction.
\end{itemize}

@@

Despite the best efforts of the prediction algorithms, a selected tactic may
not solve the current goal, proceed in the wrong direction
or even loop. For that reason, predictions need to be accompanied by a
proof search mechanism that allows for backtrac king and
can choose which proof tree to extend next and in which direction.
Our search algorithm is a Monte Carlo tree search~\cite{} algorithm that relies
on a prior evaluation function and a prior policy function. Those priors are
learned through direct supervised learning for the policy and via the data
accumulated during orthogonalization for the evaluation. Therefore, this MCTS
algorithm does not need to rely on roll outs for evaluation. The
policy and evaluation are estimated by the simple supervised k-NN algorithm
here instead of neural networks trained through reinforcement learning in
AlphaGo Zero~\cite{silver2017mastering}.
A characteristic of the MCTS algorithm is that it offers a good trade-off
between exploitation and exploration. This means that the algorithm searches
deeper more promises branches and leaves enough time for the exploration
of less likely alternatives.

>>>>

\begin{itemize}
\item Proof recording at the tactic level is made more precise. Pattern
matching constructions, opening of submodules are supported. The different
recording steps (parsing, unfolding and replaying) are regrouped into a single
\sml function.
\item Monte Carlo tree search~\cite{montecarlo} (MCTS) replaces A* as our
search algorithm. The MCTS algorithm gives a more balanced feedback on
the success of
each proof step by
comparing subtrees of the search tree instead of leafs. The policy and
evaluation are learned
through supervised learning.
\item Proof guidance required by MCTS is given by predictors for
three kinds of objects: tactics, theorems and lists of goals.
\item The orthogonalization process that eliminates redundant tactics is 
described in a precise manner.
\item A tactic abstraction mechanism is introduced. It enables us to create
more general and flexible tactics where tactic arguments are dynamically
predicted.
\item The internal ATP \metis is complemented
by asynchronous calls to \eprover to help \tactictoe during proof search.
\item First evaluation of \tactictoe success rate relative to
the length of the original human proofs.
\item Minimization and prettification of the generated proof improves user 
interaction.
\end{itemize}

@@

Despite the best efforts of the prediction algorithms, a selected tactic may
not solve the current goal, proceed in the wrong direction
or even loop. For that reason, predictions need to be accompanied by a
proof search mechanism that allows for backtrac king and
can choose which proof tree to extend next and in which direction.
Our search algorithm is a Monte Carlo tree search~\cite{montecarlo} algorithm 
that relies
on a prior evaluation function and a prior policy function. Those priors are
learned through direct supervised learning for the policy and via the data
accumulated during orthogonalization for the evaluation. Therefore, this MCTS
algorithm does not need to rely on roll outs for evaluation. The
policy and evaluation are estimated by the simple supervised k-NN algorithm
here instead of neural networks trained through reinforcement learning in
AlphaGo Zero~\cite{silver2017mastering}.
A characteristic of the MCTS algorithm is that it offers a good trade-off
between exploitation and exploration. This means that the algorithm searches
deeper more promises branches and leaves enough time for the exploration
of less likely alternatives.
